---
title: "A {fun} Intro to R Programming"
subtitle: "The basics,<br>data wrangling,<br>and more!"
output: 
  xaringan::moon_reader:
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%<br>"
      ratio: "16:9"
---


layout: true

<style>
.onehundredtwenty {
  font-size: 120%;
   }

<style>
.ninety {
  font-size: 90%;
   }

.eightyfive {
  font-size: 85%;
   }
   
.eighty {
  font-size: 80%;
   }
   
.seventyfive {
  font-size: 75%;
   }
   
.seventy {
  font-size: 70%;
   }
   
.fifty {
  font-size: 50%;
   }
   
.forty {
  font-size: 40%;
   }
</style>


```{r meta, echo=FALSE}
library(metathis)
meta() %>%
  meta_general(
    description = "Intro to R Programming",
    generator = "xaringan and remark.js"
  ) %>%
  meta_name("github-repo" = "favstats/xxx") %>%
  meta_social(
    title = "Intro to R Programming",
    # url = "https://www.favstats.eu",
    # og_type = "website",
    og_author = "Pekka Sagner",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@favstats"
  )
```

```{r setup, include=FALSE}
# dateWritten <- format(as.Date('2020-05-04'), format="%B %d %Y")
workshop_day <- format(as.Date("2021-07-09"), format="%B %d %Y")
pacman::p_load(tidyverse, fontawesome, tidyverse, knitr)
options(
    htmltools.dir.version = FALSE,
    knitr.table.format = "html",
    knitr.kable.NA = ""
)
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3 # Better figure resolution
)
# Enables the ability to show all slides in a tile overview by pressing "o"
xaringanExtra::use_tile_view()
xaringanExtra::use_panelset()
xaringanExtra::use_clipboard()
xaringanExtra::use_share_again()
xaringanExtra::style_share_again(share_buttons = "all")
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,
  mute_unhighlighted_code = FALSE
)
# xaringanExtra::use_webcam()
knitr::opts_chunk$set(warning = F, message = F) # Whether to display errors
```

---
name: title-slide
class: primary


#.fancy[`r rmarkdown::metadata$title`] 

###.fancy[`r rmarkdown::metadata$subtitle`]


<br>


Fabio Votta

[`r fa(name = "twitter", fill = "black")` @pekkato](http://twitter.com/pekkato)<br>
[`r fa(name = "github", fill = "black")` @favstats](http://github.com/pekkasagner)<br>
[`r fa(name = "link", fill = "black")` favstats.eu](https://www.favstats.eu)



`r workshop_day`

.fifty[Link to slides: [favstats.github.io/ds3_r_intro](https://favstats.github.io/ds3_r_intro)]

---

### Your friendly neighborhood R Instructor

.leftcol40[
Hallo 

]

.rightcol60[
+ Ph.D. Candidate in Political Communication at University of Amsterdam

+ Passionate about R and Data Science

+ I love to travel (when there is no pandemic)

+ I enjoy and (occasionally) create R memes

]